\thetitle

### 2009-02-23 paper/paper.tex
bib fiddling for springer
darcs-hash:20090220082649-d98fc-dae1df0194319b97160e3bab21e92b4404d48fb5.gz
paper: Specify Coq version 8.2.
Ignore-this: 3643ada754cd6280cac9daa13079a9b1

darcs-hash:20090220091248-bab43-05a80293b809e60f9a8ec0e1e238a3c9e5e9dd06.gz
paper: Correct Wadler reference, erase dangling Jones reference.
Ignore-this: 4fb42d2af3bdd6d876a741994ac111cb

darcs-hash:20090220135553-bab43-3546114a04ea4093f08e875af56930da56765195.gz
paper: Use CIC instead of pCIC. (There is no justice.)
Ignore-this: b04278ad5ea29cbfe0fb3e3f5972da88

darcs-hash:20090223154803-bab43-ffaf197fd1620f5946909

The Coq source files containing the entire formalisation can be downloaded from \url{http://www.eelis.net/research/quicksort/}. We used Coq version 8.2 beta 2.

@@

Since we are working in Coq, we already have at our disposal a full functional
programming language, in the form of Coq's pCIC \cite{coq'art}. However, just
writing the algorithm as an ordinary Coq function would not let us observe its
use of comparisons. 
We can however see comparison counting as a \emph{side effect}. As is well
known and standard practice in functional languages such as Haskell, side
effects can be represented using \emph{monads}: a side-effecting function |f|
from |A| to |B| is represented as a function |A -> M B| where |M| is a type
constructor encapsulating the side effects. ``Identity'' and ``composition''
for such functions are given by |ret| (for ``return'') of type |A -> M A| and
|bind| (infix: |>>=|) of type |M A -> (A -> M B) -> M B| satisfying certain
identities (the \emph{monad laws}). For a general introduction to monadic
programming and monad laws, see \cite{wadler93monads}.

@@

\bibliographystyle{plain}
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{paper}

>>>>

The Coq source files containing the entire formalisation can be downloaded from \url{http://www.eelis.net/research/quicksort/}. We used Coq version 8.2.

@@

Since we are working in Coq, we already have at our disposal a full functional
programming language, in the form of Coq's CIC \cite{coq'art}. However, just
writing the algorithm as an ordinary Coq function would not let us observe its
use of comparisons. 
We can however see comparison counting as a \emph{side effect}. As is well
known and standard practice in functional languages such as Haskell, side
effects can be represented using \emph{monads}: a side-effecting function |f|
from |A| to |B| is represented as a function |A -> M B| where |M| is a type
constructor encapsulating the side effects. ``Identity'' and ``composition''
for such functions are given by |ret| (for ``return'') of type |A -> M A| and
|bind| (infix: |>>=|) of type |M A -> (A -> M B) -> M B| satisfying certain
identities (the \emph{monad laws}). For a general introduction to monadic
programming and monad laws, see \cite{wadler95monads}.

@@

\bibliographystyle{splncs}
\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{paper}
